
\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Hemant Upadhyay}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{B.41/162,Siddharth Nagar,\\Goregaon(West),Mumbai-400062\\+91-8976296475}
\address{github.com/hemantupadhyay24\\hemant.upadhyay@spit.ac.in}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Sardar Patel Institute of  Technology}, Bhavans Campus, Mumbai\\
{\sl Bachelor of Engineering}, Information Technology, June 2021\hfill 
CGPA: 8.45
\\
\\
\textbf{Government Polytechnic Mumbai}, Bandra, Mumbai\\
{\sl Diploma in Engineering}, Information Technology, May 2018\hfill 
Percentage: 93.13%

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
\textbf{ModiCare-Aadhar based Digital Health Record  System}\hfill
Aug '19-Ongoing
\\
It is an online portal were citizens having Aadhaar gets enrolled into the system.Through this service, all the patient's record will get fully digitized;doctor's prescription, lab reports, etc will be online so no more manhandling with Treatment records, further it will help in Disease Detection and medication of patients.\\
Technologies : HTML/CSS,Bootstrap,PostgresSQL,Flask,SkyScannerAPI,Char.js.
\par
\textbf{EuroWings,your travel-mate!}\hfill Jan '19 - April '19\\
Designed as a complete platform for travel. The website provides everything needed to assist users with their travel plans, including choosing transportation, hotel booking, discovering local venues, and managing expenses. \\
Technologies : HTML/CSS,Bootstrap,PostgresSQL,Flask,SkyScannerAPI,Char.js.
\par
\textbf{Gyaan - Learning Management System}\hfill Aug '18 - Nov '19\\
It's LMS where students can log in to register themselves to specific courses, attempt quiz, see their scoreboard and based on that give feedback to the lecturer. \\
Technologies : HTML,Materialize CSS,Chart.JS,PHP,MySQL.

\par
\textbf{Geofencing with Task Management}\hfill Nov '17 - April '18\\
The app uses the geofence concept for checking whether the teacher is present in the college or not.If she's not available then changing the schedule of teacher's timetable,setting the main time table directly by exporting the excel file,checking whether the teacher is actually taking lecture or not by scanning the QR code 
Technologies : Android Studio,HTML/CSS,PHP,MySQL,RadarAPI,SheetsAPI.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}

\textbf{Languages}: C, C++, Java, Python, Bash, SQL, LaTeX.
\\
\textbf{Web Development}: HTML, CSS, Materialize CSS,Bootstrap, JavaScript, PHP, Flask, Django, PostgresSQL, MySQL, Android Studio.
\\
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%	Awards & Achievements
%-------------------------------------------------------------------------------
\section{ACHIEVE\\-MENTS}
\textbf{Awarded the Bronze Medal} for state-level project competition at BabaSaheb Gadwe Institute of Technology,Churchgate ’18\\
\textbf {Guinness World Record Holder}(Most Bangles put into Hand in 30 seconds \& Largest Newspaper Boat)\\
\textbf{Second Runner-up} in State Level Technical Paper Presentation on topic IoT(Internet of Things) \\
\textbf {Chairperson and Organizer of Techkriti'17} - Cultural & Technical State level fest of GPMumbai.\\
\textbf {Debater of the year} awarded in 2015,proud participant of INMUN(Indian Model United nations) held in year 2015.

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	Interests
%-------------------------------------------------------------------------------
\section{INTERESTS}
Competitive Programming, Cooking, Reading, Sketching, Social/ Volunteering Work
%-------------------------------------------------------------------------------

\end{resume}
\end{document}